Results

### 2021-07-08 Analysis/03_Summarise_results.Rmd
Update 03_Summarise_results.Rmd

"TPD_Richness"            
"TPD_Evenness"            
"TPD_Divergence"

>>>>

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "TPD_Richness", level.names = removals, col = cols, legend.pos = "bottomright")
```

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "TPD_Evenness", level.names = removals, col = cols, legend.pos = "bottomright")
```

### Divergence

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "TPD_Divergence", level.names = removals, col = cols, legend.pos = "bottomright")
```
